Volunteers in the Clouds: A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2015-12-10 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
fixing an acronym

This optimization problem was selected because it is representative of the kind of
algorithms, data types, and structures employed in large scale optimization problems. 
The function was implemented in both Matlab and Java languages as part of the
Test Suite of the companion competition of the Special Session and to give competitors an idea of the
computational cost of the challenge, the runtime required for 10,000 function 
evaluations (FEs) for a particular configuration was published by organizers. The Java
implementation took 7596ms and the Matlab version 1115ms. The whole experiment had the value of
3,000,000 FEs as termination condition. Using the Java implementation as
a guide, the function described above was implemented to compare the performance of JavaScript against
both implementations, again using the time required for 10,000 FEs. 
Before discussing the setup and performance results, certain details of
the implementation in JavaScript are presented to give readers an idea of 
how practical and mature this language is for developing complex mathematical functions.

@@

We found that the JavaScript ecosystem is mature enough for developing non-trivial 
code, but developers have to consider the differences between VMs implementations
and therefore use certain libraries in order to increase the precision and repeatability of
algorithms. As for the performance of JavaScript against Java and Matlab
we conducted first the basic test described earlier in a 3.7 GHz Quad-Core
Intel Xeon E5 processor running OS X 10.10.5, 
using Java(TM) SE Runtime Environment (build 1.8.0\_25-b17), 
MatLab version R2015a for Mac OSX, Node FrameWork version 0.12.2,
Google Chrome Version 46.0.2490.86 (64-bit) 
and Firefox version 41.0.2. % (Paloma) Table here? Or at least the characteristics could be represented the same way as for the baseline experiment
 The performance of the time required for 10,000 FEs is presented in
Figure \ref{fig:f15_times}. In our test the Matlab implementation had the best
performance with an average of 935ms, followed by Java with
991ms. On the other hand, JavaScript took 32\% more time than Java with 1238ms in Chrome using a 
single Web Worker and 1,234ms using Node.js. % Are these results correct? JS=>1240ms and Node.js=>1,270ms ???
The results also show that there is not much difference between the Node.js
implementation an that of a
browser. There is also not much difference between running the code in the main thread or in Web
Workers. When running the experiment in Firefox a dialog alerted that the
script was taking too much time, showing that this
kind of processing is not intended for the main thread. Additionally, there is not much overhead
when running two
Web Workers in parallel as they took 1279ms each. This experiment
shows that JavaScript is viable as a language
language for developing complex mathematical functions an these can run in a browser
with acceptable performance. 
\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\linewidth]{f15_times.png}
\caption{ Runtime of 10,000 function evaluations (FEs) for $F_{15}$} 
\label{fig:f15_times}
\end{figure}

>>>>

This optimization problem was selected because it is representative of the kind of
algorithms, data types, and structures employed in large scale optimization problems. 
The function was implemented in both Matlab and Java languages as part of the
Test Suite of the companion competition of the Special Session and to give competitors an idea of the
computational cost of the challenge, the runtime required for 10,000 function 
evaluations for a particular configuration was published by organizers. The Java
implementation took 7596ms and the Matlab version 1115ms. The whole experiment had the value of
3,000,000 function evaluations as termination condition. Using the Java implementation as
a guide, the function described above was implemented to compare the performance of JavaScript against
both implementations, again using the time required for 10,000 function evaluations. 
Before discussing the setup and performance results, certain details of
the implementation in JavaScript are presented to give readers an idea of 
how practical and mature this language is for developing complex mathematical functions.

@@

We found that the JavaScript ecosystem is mature enough for developing non-trivial 
code, but developers have to consider the differences between VMs implementations
and therefore use certain libraries in order to increase the precision and repeatability of
algorithms. As for the performance of JavaScript against Java and Matlab
we conducted first the basic test described earlier in a 3.7 GHz Quad-Core
Intel Xeon E5 processor running OS X 10.10.5, 
using Java(TM) SE Runtime Environment (build 1.8.0\_25-b17), 
MatLab version R2015a for Mac OSX, Node FrameWork version 0.12.2,
Google Chrome Version 46.0.2490.86 (64-bit) 
and Firefox version 41.0.2. % (Paloma) Table here? Or at least the characteristics could be represented the same way as for the baseline experiment
 The performance of the time required for 10,000 function evaluations is presented in
Figure \ref{fig:f15_times}. In our test the Matlab implementation had the best
performance with an average of 935ms, followed by Java with
991ms. On the other hand, JavaScript took 32\% more time than Java with 1238ms in Chrome using a 
single Web Worker and 1,234ms using Node.js. % Are these results correct? JS=>1240ms and Node.js=>1,270ms ???
The results also show that there is not much difference between the Node.js
implementation an that of a
browser. There is also not much difference between running the code in the main thread or in Web
Workers. When running the experiment in Firefox a dialog alerted that the
script was taking too much time, showing that this
kind of processing is not intended for the main thread. Additionally, there is not much overhead
when running two
Web Workers in parallel as they took 1279ms each. This experiment
shows that JavaScript is viable as a language
language for developing complex mathematical functions an these can run in a browser
with acceptable performance. 
\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\linewidth]{f15_times.png}
\caption{ Runtime of 10,000 function evaluations for $F_{15}$} 
\label{fig:f15_times}
\end{figure}
